\documentclass[letter]{res}
\newcommand\tab[1][0.5cm]{\hspace*{#1}}
\setlength{\textheight}{9.5in}
%\usepackage{fontspec}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\geometry{
 a4paper,
 total={210mm,297mm},
 left=20mm,
 right=25mm,
 top=15mm,
 bottom=15mm,
 bindingoffset=0mm
 }\usepackage{fontenc}
\usepackage{enumitem}
\usepackage{hyperref}
\setlist{nolistsep}
\usepackage[colorinlistoftodos]{todonotes}
%\setmainfont[Mapping=tex-text]{Linux Libertine O}
\begin{document}
\name{Khanh V. Le\\[15pt]}
\begin{resume}
  \noindent\makebox[\linewidth]{\rule{\paperwidth}{0.5pt}}
\section{Contacts}\vspace{1mm}
{\sl Address:}$\>$ {\tab12345 John Street, Bay Area CA, 12345}\hfill{\sl Mobile:  \tab} {(+1) 000 - 000 - 0000}\\
{\sl Github:}$\>$  \tab\href{https://www.github.com/khanhle10}{ https://github.com/khanhle10}\hfill{\sl Email:\hspace{4mm}}$\>$ {gmail@gmail.com}\\
{\sl LinkedIn:}$\>$\tab\href{https://www.linkedin.com/pub/khanh-le/97/609/593}{https://linkedin.com/khanhle}
\hfill{\sl Homepage:\hspace{8mm}}$\>$ \href{http://www.kvle10.xyz}{http://kvle10.xyz}
\section{Education}\vspace{1mm}
{\sl Bachelors of Computer Science} - Software Engineering\hfill Graduated: May 27, 2016\\
{\sl Minor} - Mathematics \\
San Francisco State University, San Francisco, CA 94132\hfill \href{http://cs.sfsu.edu/}{https://sfsu.edu}
\section{Skills}
\vspace{1mm}
{\sl Programming Languages}\hspace{1em} C/C++, Java, Ruby, and Python\\
{\sl Web Languages}\hspace{5em} HTML5, CSS3, PHP, JavaScript, and Ruby on Rails\\
{\sl Operating Systems}\hspace{4em}Linux/Unix systems, Windows, and OS \\
{\sl Design \& IDE Tools}\hspace{3em} Visual Studio, VIM, Android Studio, Netbeans, Sublime, Atoms, and Eclipse \\
{\sl Software}\hspace{8.5em}LaTex, Git, SVN, Bootstrap, AngularJS, NodeJS, ExpressJS, and RESTful
\section{Projects}
\vspace{1mm}
AlpacaTable - Software Engineering Web Design\vspace{1mm}
\begin{itemize}
 \item I was part of 6 man team developing a restaurant reservation website called \href{ http://www.sfsuswe.com/~f15g07/index.php}{AlpacaTable} utilizing LAMP stack and Agile Development Environment.
\item I was responsible for integrating all front-end user interface (UI) with back-end PHP to make a more fluid website as well as creating UML diagram for the front page, Login, and SignUp page. Coded mostly in JavaScript, CSS, and HTML with some PHP.
\vspace{1.5mm}
\appendix{HTML, CSS, PHP, MySQL, JavaScript, Apache, Bootstrap and SVN version control.}
 \end{itemize}
Deuce Card Game - Internet Application Web Design\vspace{1mm}
\begin{itemize}
 \item I was part of 4 man development team building a multi-player web card game called Deuce with real time chat interface using Ruby on Rails application, Ajax, and deployed on Heroku Cloud Platform.
 \item  I was the team-lead and tech-lead responsible for building the real time chat user interface(UI) using Ajax and Pusher API, setting up Model View Controller framework to generate and track unique users throughout the process of creating a game or joining an existing game within a lobby, and lastly, setting up the database using PostgreSQL to store user data and game images. Coded mostly in CSS, JavaScript, HTML, and Ruby.
 \vspace{1.5mm}
\appendix{Ruby on Rails, JavaScript, CSS3, PostgreSQL, HTML5, PhaserJS, Pusher API, Bootstrap, Git, Heroku Cloud Platform, and Ajax}
 \end{itemize}
 ParkIt - Android App \vspace{1mm}
\begin{itemize}
 \item I was part of a 6 man team developing an Android app called ParkIt using singleton design pattern, Google Map API, Agile Design Development, and San Francisco City JSON database to display detailed information such as street cleaning time and ticket charged.
 \item I was responsible for user interface (UI), Google Map view, and UML Diagram. Coded mostly in Java and XML.
 \vspace{1.5mm}
\appendix{JSON, Google API, Java, XML, Singleton Design Pattern, and Android Studio.}
 \end{itemize}
\section{Activities \& Experienced}
\vspace{1mm}
 Teaching Associates and Lab IT Manager at SFSU 2014 - 2016 / 2015 - 2016 \vspace{1mm}
\begin{itemize}
\item Held lectures and office hours in the course of Introductory to Java.
\item Maintain Computer Science Department Lab equipment and troubleshoot issues both software and hardware.
\end{itemize}
Association for Computing Machinery (ACM) 2015 - 2016 Officer \vspace{1mm}
 \begin{itemize}
\item Organized and conduct lectures on Android Development, Git, and how to setup Apache2 server to build a simple website.
\end{itemize}
\end{resume}
\end{document}
